\section{General view of internship}

\subsection{Introducing company}
\textbf{SMILE} (\textbf{\color{blue}\url{https://www.smile.eu/en}}) is the 1st integrator and European expert in open source solutions. 

SMILE advertises 4 different services :
\begin{enumerate}
	\item \textbf{DIGITAL : } creates websites, mobile apps and collaborative software. 
	\item \textbf{BUSINESS APPS : } which collects all business activities of customers allowing them to get better insight into their data and be more efficient. 
	\item \textbf{EMBEDDED \& IOT : } which builds software for innovative smart objects.
	\item \textbf{OUTSOURCING : } ports data into private cloud computing. 
\end{enumerate}


\begin{center} \color{red}
I'm part of \textbf{EMBEDDED \& IOT} division.
\end{center}

\textbf{SMILE} has over than 1300 employees (\textbf{Smilers}) across 7 different countries (\textit{France, Belgium, Switzerland, Luxembourg, Netherlands, Ukraine and Morocco}).

\subsection{Internship objectives}
In order to offer the best experience for \textbf{SMILE}'s clients, We require :

\begin{itemize}
\item[$\bullet$] Test our solutions before production to detect faulty code and anticipate bugs.
\item[$\bullet$] Troubleshoot errors that raise during production. 
\item[$\bullet$] Pointing-out sources of latencies (\emph{disk, network, scheduler, ..., etc}), memory leaks, kernel panics and many more.
\item[$\bullet$] Handle potential malicious code infections and being able to respond.
\end{itemize}

  
\subsection{Internship pre-requests}

The pre-requests of the internship are : 
\begin{itemize}
	\item[$\ast$] {Good skills on C/C++ and Python.}
	\item[$\ast$] {Working on Linux environment, basic Linux kernel is recommended.}
	\item[$\ast$] {Background electrical and electronics engineering concepts}
\end{itemize}


\subsection{Internship requirements}
The request document of the intership stressed out on experimenting and documenting the following points :

\begin{enumerate}
	\item \textbf{Userspace debugging methodologies : } maily for C/C++ (using GDB, strace, ptrace, ltrace, valgrind)
	
	\item \textbf{Kernel-land code debugging : } using KGDB/KDB, kernel oops, magic SysRQ, OpenOCD (with focus on it's syntax).
	
	\item \textbf{Tracing and profiling : } to increase software quality, instrumentation must be used with tools like : \textbf{Ftrace (trace-cmd)}, \textbf{Perf} and \textbf{LTTng}.\\
Those tracers must be compared  to choose the appropriate one for a particular situation.

	\item \textbf{Testing platforms : } known boards must be used (\textit{Raspberry PI 3}, \textit{Beagle bone black wireless} and \textit{I.MX6}).
	
	\item \textbf{Documentation : } providing step by step manual for every tool to be used by engineers at project's developement lifecycle and maintenance.
\end{enumerate}


\begin{center}\Large
\color{red}In short, the goal of the internship is to reduce Linux debugging time.
\end{center}

